Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-29 paper/ijcai16.tex
paper: fix typo.

We compare {\sc SetMargin} against three state-of-the-art Bayesian
approaches: i) the Bayesian approach from \cite{guo2010real},
selecting queries according to {\em restricted informed VOI} ({\sc
  riVOI}), a computationally efficient heuristic approximation of
value-of-information, and inference using TrueSkill$^{TM}$
\cite{HerbrichMG06} (an inference scheme based on expectation
propagation \cite{Minka01}); ii) the Bayesian framework of
\cite{viappiani2010optimal} using Monte Carlo methods (with 50,000
particles) for Bayesian inference and asking choice queries
(i.e. selection of the most preferred item in a set) selected
optimizing {\em Expected Utility of a Selection} (a tight
approximation for the value of information, hereafter just called {\sc
  EUS}); iii) {\em Query Iteration} (referred as {\sc QI} below), also
from \cite{viappiani2010optimal}, an even faster query selection
method which repeateadly samples a set of utility vectors according to
their beliefs and forms a query set selecting the items that maximize
utility for each of the vectors.

>>>>

We compare {\sc SetMargin} against three state-of-the-art Bayesian
approaches: i) the Bayesian approach from \cite{guo2010real},
selecting queries according to {\em restricted informed VOI} ({\sc
  riVOI}), a computationally efficient heuristic approximation of
value-of-information, and inference using TrueSkill$^{TM}$
\cite{HerbrichMG06} (an inference scheme based on expectation
propagation \cite{Minka01}); ii) the Bayesian framework of
\cite{viappiani2010optimal} using Monte Carlo methods (with 50,000
particles) for Bayesian inference and asking choice queries
(i.e. selection of the most preferred item in a set) selected
optimizing {\em Expected Utility of a Selection} (a tight
approximation for the value of information, hereafter just called {\sc
  EUS}); iii) {\em Query Iteration} (referred as {\sc QI} below), also
from \cite{viappiani2010optimal}, an even faster query selection
method which repeatedly samples a set of utility vectors according to
their beliefs and forms a query set selecting the items that maximize
utility for each of the vectors.
